\documentclass[journal]{IEEEtran}

\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows.meta, positioning, fit, backgrounds, calc}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{hyperref}
\usepackage{subcaption}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

\begin{document}

\title{BridgeSentry: LLM-Guided Vulnerability Discovery in Cross-Chain Bridges via Semantic Modeling and Synchronized Dual-Chain Fuzzing}

% \author{
% \IEEEauthorblockN{Tuan-Dung Tran\IEEEauthorrefmark{1}\IEEEauthorrefmark{2}}
% \IEEEauthorblockA{
% \IEEEauthorrefmark{1}University of Information Technology, VNU-HCM, Ho Chi Minh City, Vietnam\\
% \IEEEauthorrefmark{2}Corresponding Author: dungtrt@uit.edu.vn
% }
% }

\maketitle

\begin{abstract}
Cross-chain bridges have become critical infrastructure in the multi-chain blockchain ecosystem, yet they remain the single largest source of financial loss in decentralized finance. Cumulative damages from cross-chain bridge exploits have reached nearly \$4.3 billion since 2021, driven by vulnerabilities that span multiple blockchains and off-chain relay components. Existing security tools address this problem only partially: static analyzers detect single-contract vulnerabilities, single-chain fuzzers explore on-chain state spaces, and graph-based frameworks classify attack transactions after exploitation has occurred. None of these tools proactively discovers logic vulnerabilities arising from cross-chain state inconsistencies. This paper presents BridgeSentry, a framework that couples large language model reasoning with synchronized dual-chain fuzzing to discover cross-chain bridge vulnerabilities before they are exploited. BridgeSentry operates in three stages. First, an LLM-based semantic extractor analyzes bridge smart contract source code and constructs Atomic Transfer Graphs, following the formal model of D\"ubler et al., to capture intended protocol invariants across source and destination chains. Second, a retrieval-augmented generation module, populated with structured knowledge from documented cross-chain exploits, generates plausible attack scenarios reflecting rational adversarial incentives. Third, a synchronized dual-EVM fuzzing engine executes these scenarios on paired blockchain instances with consistent snapshot management, using semantic waypoints to guide exploration toward cross-chain invariant violations. We evaluate BridgeSentry on a benchmark of 12 reconstructed real-world cross-chain bridge exploits, covering Wormhole, Nomad, PolyNetwork, and nine additional incidents, over 20 independent runs per benchmark (240 runs total) of real-bytecode dual-EVM fuzzing on forked mainnet state. BridgeSentry detects all 12 target vulnerabilities on every one of the 240 runs, with a median time-to-exploit of 1.2\,s (per-bridge medians ranging from 0.5\,ms to 4.9\,s). For context, the original baseline tools (ItyFuzz, SmartShot, VulSEye, SmartAxe, GPTScan, XScope) detect at most one of the twelve cross-chain incidents per their publicly reported per-bridge results, reflecting that none was designed for coordinated dual-chain execution. To enable a per-bridge comparison absent public artifacts, we re-implement four of these tools and run them on the same 12 benchmarks; under a stricter predicate-level matching criterion the re-implementations attain 12/12 (SmartShot), 10/12 (XScope), 9/12 (VulSEye), and 4/12 (SmartAxe), with the static analyzer's gap concentrated on runtime off-chain key-compromise cases. These results indicate that cross-chain detection hinges on the dual-chain modeling and LLM-derived invariants that BridgeSentry contributes, while the most exploit-faithful guidance among dynamic strategies remains an open comparison we quantify in Section~\ref{sec:experiments}.
\end{abstract}

\begin{IEEEkeywords}
Cross-chain bridge, vulnerability detection, smart contract fuzzing, large language model, blockchain security
\end{IEEEkeywords}

% ============================================================
\section{Introduction}
% ============================================================

The expansion of blockchain technology beyond single-chain architectures has given rise to a multi-chain ecosystem in which decentralized finance (DeFi) applications operate across heterogeneous networks such as Ethereum, Binance Smart Chain, and Solana~\cite{belchior2021survey, augusto2024sok}. Cross-chain bridges serve as the primary infrastructure enabling asset transfers and message passing between these networks. By locking tokens on a source chain and minting equivalent representations on a destination chain, bridges allow users to move value across otherwise isolated ledgers.

However, bridges have also become the most lucrative targets for attackers. According to Wu et al.~\cite{wu2025safeguarding}, cumulative losses from cross-chain bridge exploits have reached nearly \$4.3 billion since 2021, with the Ronin Network at \$624M, PolyNetwork at \$611M, and Wormhole at \$326M among the costliest incidents~\cite{augusto2024sok, lee2023sok}. These attacks exploit a diverse range of vulnerabilities: access control bypasses in validator contracts, improper initialization of verification logic, fake deposit events accepted by off-chain relays, and reentrancy conditions triggered through cross-chain callback sequences~\cite{liao2024smartaxe, duan2023attacks}.

The central technical challenge is state explosion. A bridge execution is not a single contract trace, but a product state over a source chain, a destination chain, and a relay. Each domain has its own storage, block time, finality assumptions, authorization logic, message queues, and failure modes. Naively fuzzing this product state by mutating transactions independently on each chain quickly becomes intractable: most generated executions are semantically irrelevant, while vulnerable executions require precise causal relationships such as ``deposit event observed, relay message malformed, destination proof accepted.'' Conversely, reducing the problem to a single chain discards exactly the cross-chain inconsistencies that make bridge exploits possible.

Existing security tools address this problem only partially. Static analyzers such as SmartAxe~\cite{liao2024smartaxe} detect cross-chain-specific vulnerability patterns in smart contract source code, but they cannot exercise runtime state transitions across two ledgers and a relay. Rule-based monitors such as XScope~\cite{zhang2022xscope} identify predefined attack signatures in transaction logs, but they operate after transactions have occurred and are constrained by hand-written rules. Graph-based systems such as BridgeGuard~\cite{wu2025safeguarding} and BridgeShield~\cite{lin2025bridgeshield} model observed cross-chain behavior, but they are primarily post-hoc classifiers rather than proactive vulnerability discovery engines. Single-chain fuzzers such as ItyFuzz~\cite{shou2023ityfuzz} and SmartShot~\cite{liang2025smartshot} reduce redundant exploration through snapshots, yet they do not model synchronized source-chain, relay, and destination-chain semantics. LLM-assisted tools such as GPTScan~\cite{sun2024gptscan} and the multi-agent system of Wei et al.~\cite{wei2025llm} improve semantic understanding, but they target individual contracts and do not provide a formal guarantee that LLM-generated invariants are logically consistent with the bridge protocol.

This limitation motivates the design principle behind BridgeSentry: the LLM should guide exploration, not serve as an unchecked oracle. We use the LLM to summarize protocol intent, construct candidate Atomic Transfer Graphs (ATGs), and propose candidate invariants and attack scenarios. These candidates are then constrained by formal validation before they influence fuzzing. At the protocol level, the extracted source-chain, relay, and destination-chain state machines are translated into a TLA+-style transition model, and model checking is used to reject invariants that are inconsistent with the intended cross-chain protocol. At the code level, symbolic execution is used as a second validation layer to check whether the surviving invariants are compatible with the smart-contract implementation. Only invariants that pass these validation gates are compiled into executable oracles and semantic waypoints for the fuzzer. In this way, LLM reasoning reduces the search space, while formal verification limits hallucination and prevents unsupported semantic assumptions from steering the dynamic analysis.

BridgeSentry addresses the remaining capability gap by combining formally validated semantic modeling with synchronized cross-chain fuzzing. Rather than exploring arbitrary transaction sequences in the full product state, BridgeSentry focuses the fuzzer on protocol-relevant regions: message creation, relay parsing, authorization checks, replay protection, and asset-conservation boundaries. The resulting workflow turns the cross-chain state explosion problem into a guided search over formally screened protocol invariants and historically grounded attack hypotheses.

This paper presents BridgeSentry as a framework that integrates four coordinated modules:

\begin{enumerate}
    \item A semantic extractor that uses an LLM to parse bridge smart contract source code and off-chain relay logic, producing Atomic Transfer Graphs~\cite{dubler2025atg} annotated with protocol-level invariants covering asset conservation, event ordering, and authorization dependencies across source chain, relay, and destination chain components.
    \item A retrieval-augmented attack scenario generator that queries a structured knowledge base of documented cross-chain exploits---drawn from the 51-event catalog of Wu et al.~\cite{wu2025safeguarding} together with the SmartAxe and XScope corpora~\cite{liao2024smartaxe, zhang2022xscope, augusto2024sok}---to produce plausible, economically motivated attack sequences targeting the identified invariants.
    \item A synchronized dual-chain fuzzing engine that maintains paired EVM instances connected through a mock relay, executes generated attack scenarios as guided seeds, and uses semantic waypoints to steer the fuzzer toward states where cross-chain invariants are likely violated.
\end{enumerate}

The principal contributions of this work are as follows:

\begin{itemize}
    \item We formulate cross-chain bridge fuzzing as a state-explosion problem over the product of source-chain, relay, and destination-chain state machines, and show how LLM-derived ATGs provide a compact semantic search space for dynamic vulnerability discovery.
    \item We introduce a formally validated invariant pipeline in which LLM-generated protocol invariants are screened by TLA+-style model checking and smart-contract symbolic execution before being used as fuzzing oracles.
    \item We adapt the Atomic Transfer Graph formalism of D\"ubler et al.~\cite{dubler2025atg} to the cross-chain bridge fuzzing setting by defining domain-specific invariant categories and compiling validated invariants into executable assertions and semantic waypoints.
    \item We design a synchronized snapshot mechanism for consistent state management across dual EVM instances and a mock relay, ensuring that the fuzzer explores cross-chain state spaces without introducing artificial inconsistencies.
    \item We evaluate BridgeSentry on 12 reconstructed real-world exploits covering source-chain, off-chain, and destination-chain attack surfaces, and---because most baselines lack runnable artifacts on this benchmark---re-implement four of them to obtain a per-bridge comparison, showing that out-of-the-box tools do not handle cross-chain incidents and that detection becomes feasible only once cross-chain modeling is supplied.
\end{itemize}

The remainder of this paper is organized as follows. Section~\ref{sec:related} reviews related work on cross-chain bridge security, smart contract fuzzing, and LLM-assisted vulnerability detection. Section~\ref{sec:problem} formalizes the problem. Section~\ref{sec:method} details the BridgeSentry methodology. Section~\ref{sec:experiments} presents the experimental evaluation. Section~\ref{sec:discussion} discusses limitations and future directions, and Section~\ref{sec:conclusion} concludes.

% ============================================================
\section{Related Work}\label{sec:related}
% ============================================================

\subsection{Cross-Chain Bridge Security Analysis}

The security landscape of cross-chain bridges has been surveyed extensively. Augusto et al.~\cite{augusto2024sok} provided a systematization of knowledge covering interoperability protocols, cataloging vulnerability classes and privacy leakage vectors across 34 cross-chain systems. Duan et al.~\cite{duan2023attacks} classified attack vectors against cross-chain systems and mapped defense mechanisms to protocol layers. Li et al.~\cite{li2025blockchain} examined challenges and future directions specific to bridge security, highlighting the tension between decentralization, performance, and auditability.

On the detection side, XScope~\cite{zhang2022xscope} defined three categories of cross-chain bridge security properties and built a rule-based detection engine operating on transaction event logs. While effective for known attack patterns on EVM-compatible chains, its detection capability degrades when logs are unavailable or when attack patterns evolve. SmartAxe~\cite{liao2024smartaxe} introduced fine-grained static analysis tailored to cross-chain vulnerabilities (CCVs), constructing cross-chain data flow graphs and taint propagation rules to detect issues such as unauthorized minting and inconsistent state validation. SmartAxe reported detection of 88 CCVs from real attacks but is inherently limited to vulnerabilities detectable through source code analysis alone.

BridgeGuard~\cite{wu2025safeguarding} pioneered graph-based detection of cross-chain attack transactions by modeling transaction execution traces as graphs and applying both global and local graph mining. BridgeShield~\cite{lin2025bridgeshield} extended this approach by constructing cross-chain behavior heterogeneous graphs (xBHGs) that unify source chain, off-chain relay, and destination chain entities, achieving an F1-score of 92.58\% across 51 real-world attack events. Zhou et al.~\cite{zhou2025bridgeguard} proposed a symbolic dataflow analysis framework for detecting external interaction vulnerabilities in bridge router contracts. Lin et al.~\cite{lin2025connector} developed Connector, a tool for automatically associating cross-chain transactions across bridges to support traceability and forensic analysis. These works demonstrate the value of multi-chain modeling, but all operate as post-hoc classifiers on observed transaction data rather than as proactive vulnerability discovery tools.

\subsection{Smart Contract Fuzzing}

Fuzzing has emerged as a primary technique for discovering vulnerabilities in smart contracts. ItyFuzz~\cite{shou2023ityfuzz} introduced snapshot-based state management to avoid re-executing long transaction sequences. This enables rapid state exploration and has detected real-world vulnerabilities, including the Nomad bridge exploit, in sub-second timeframes. VulSEye~\cite{liang2025vulseye} proposed stateful directed graybox fuzzing that combines static target identification with dynamic reachability testing. Midas~\cite{ye2024midas} extended fuzzing to discover profit-generating exploits through feedback-driven exploration and differential analysis against reference implementations.

Recent work also explores richer guidance signals. Kong et al.~\cite{kong2025fuzzing} introduced Verite, which directs fuzzing toward profitable vulnerability patterns using gradient-descent-based profit maximization over on-chain transaction data. This economic reward differs from BridgeSentry's semantic waypoint guidance: Verite optimizes for attacker profit, while BridgeSentry optimizes for cross-chain invariant violation. SmartShot~\cite{liang2025smartshot} introduced mutable snapshots that allow the fuzzer to mutate captured states, expanding the reachable state space beyond sequential transaction exploration and achieving up to 20.2x speedup over prior snapshot approaches. Chen et al.~\cite{chen2024gpufuzzing} demonstrated GPU-accelerated smart contract fuzzing through incremental snapshot designs. Qin et al.~\cite{qin2025epg} proposed Execution Property Graphs as a unified representation integrating multiple static analysis views to enhance dynamic testing. Wu et al.~\cite{wu2024fuzzers} provided a comprehensive empirical comparison of smart contract fuzzers and highlighted the trade-offs between coverage strategies and vulnerability detection rates.

Despite these advances, all existing fuzzers operate on a single blockchain instance and cannot natively model the paired state transitions and relay communication that define cross-chain bridge execution semantics.

\subsection{LLM-Assisted Vulnerability Detection}

The application of large language models to smart contract security has grown rapidly. GPTScan~\cite{sun2024gptscan} demonstrated that combining GPT-based semantic reasoning with static analysis confirmation can detect logic vulnerabilities that purely syntactic tools miss, discovering 9 previously unknown vulnerabilities in audited contracts. Wei et al.~\cite{wei2025llm} proposed a multi-agent LLM system for end-to-end vulnerability detection, achieving state-of-the-art results on standard benchmarks by decomposing the analysis pipeline into specialized agent roles. Liu et al.~\cite{liu2023gnn} combined GNN-based structural analysis with expert-defined vulnerability patterns, using knowledge graphs to inject domain knowledge into the detection process. Zhuang et al.~\cite{zhuang2021gnn} first demonstrated GNN-based vulnerability detection on contract graphs constructed from control flow and data flow representations. Chen et al.~\cite{chen2023semantic} proposed semantic graphs combined with residual GCNs and edge attention for multi-type vulnerability detection. Wang et al.~\cite{wang2019han} introduced the heterogeneous graph attention network (HAN) architecture that BridgeShield subsequently adapted for cross-chain transaction modeling.

The convergence of LLMs and fuzzing remains underexplored in the cross-chain context. Ali et al.~\cite{ali2025crossguard} combined runtime-adaptive LLM guidance with cross-contract fuzzing in a single-chain setting, demonstrating the potential of LLM-directed dynamic testing for complex DeFi logic. Their system uses LLM feedback to adjust mutation strategies during fuzzing based on execution outcomes, achieving improved detection of inter-contract vulnerabilities on single-chain protocols. BridgeSentry shares the principle of using LLM reasoning to guide fuzzing but differs in three respects: first, BridgeSentry operates across two synchronized blockchain instances rather than a single chain; second, it uses the LLM in a preprocessing stage to construct ATGs and generate attack scenarios rather than as a runtime feedback loop; and third, it targets cross-chain invariant violations that arise from state inconsistencies between chains, a vulnerability class not addressed in single-chain settings.

\subsection{Atomic Transfer Graphs}

The Atomic Transfer Graph formalism was introduced by D\"ubler et al.~\cite{dubler2025atg} as a framework for designing secure-by-construction cross-chain protocols over heterogeneous blockchain ecosystems. Their work defines ATGs as directed labeled graphs over blockchain entities and transfer operations, and provides formal security proofs for protocols constructed under the ATG model. BridgeSentry applies ATGs in a different context: rather than using ATGs to design new protocols, we use them to model existing bridge implementations and derive testable invariants for dynamic vulnerability discovery. The four invariant categories we define, which are detailed in Section~\ref{sec:problem}, are specific to the cross-chain bridge fuzzing setting and complement the protocol-design guarantees of the original ATG framework.

Table~\ref{tab:rw-positioning} summarizes representative tools along the dimensions emphasized in our introduction: analysis modality, whether coordinated source/destination/relay execution is exercised in a single harness, use of dynamic fuzzing, and the role of LLMs (if any).

\begin{table*}[!t]
    \centering
    \caption{Representative tools compared by analysis modality, dual-chain harness with relay ($\mathcal{C}_S{+}\mathcal{C}_D{+}\mathcal{R}$), dynamic fuzzing, and LLM role. Column meanings and artifact scope are given below the table.}
    \label{tab:rw-positioning}
    \small
    \setlength{\tabcolsep}{6pt}
    \renewcommand{\arraystretch}{1.25}
    \begin{tabular*}{\textwidth}{@{\extracolsep{\fill}}llccc@{}}
      \toprule
      \textbf{Tool / framework} & \textbf{Modality} & \textbf{Dual\,+\,$\mathcal{R}$} & \textbf{Fuzz} & \textbf{LLM} \\
      \midrule
      SmartAxe~\cite{liao2024smartaxe}      & Stat.  & --- & --- & --- \\
      XScope~\cite{zhang2022xscope}         & Obs.   & --- & --- & --- \\
      BridgeGuard~\cite{wu2025safeguarding} & Obs.   & --- & --- & --- \\
      BridgeShield~\cite{lin2025bridgeshield} & Obs. & --- & --- & --- \\
      ItyFuzz~\cite{shou2023ityfuzz}        & Fuzz   & --- & \checkmark & --- \\
      SmartShot~\cite{liang2025smartshot}   & Fuzz   & --- & \checkmark & --- \\
      GPTScan~\cite{sun2024gptscan}         & Stat.  & --- & --- & Prep. \\
      CrossGuard~\cite{ali2025crossguard}   & Fuzz   & --- & \checkmark & In-loop \\
      \textbf{BridgeSentry} (Sec.~\ref{sec:method}) & Stat.\,+\,Fuzz & \checkmark & \checkmark & Prep. \\
      \bottomrule
    \end{tabular*}\\[0.6em]
    \begin{minipage}{\textwidth}\footnotesize\raggedright
      \textbf{Columns.} \emph{Modality}---\textbf{Stat.}: design-time analysis on source or specifications (taint, data-flow, or LLM-on-source); \textbf{Obs.}: detection driven by on-chain traces, logs, or transaction graphs; \textbf{Fuzz}: dynamic greybox execution.
      \emph{Dual\,+\,$\mathcal{R}$}: coordinated dual-chain execution with explicit relay (or equivalent messaging) in one harness (Section~\ref{sec:problem}).
      \emph{LLM}: \textbf{---}\,none; \textbf{Prep.}\,offline modeling or scenario generation; \textbf{In-loop}\,runtime feedback during fuzzing.
      \emph{Artifact:} the research prototype implements Module~4 end-to-end from structured ATG, invariant, and hypothesis JSON artifacts; Modules~1--3 match Section~\ref{sec:method} at the component-interface level.
    \end{minipage}
  \end{table*}

% ============================================================
\section{Problem Formulation}\label{sec:problem}
% ============================================================

\subsection{Cross-Chain Bridge Execution Model}

A cross-chain bridge protocol $\mathcal{B}$ operates across three execution domains: a source chain $\mathcal{C}_S$, a destination chain $\mathcal{C}_D$, and an off-chain relay component $\mathcal{R}$. A complete cross-chain transfer proceeds through the following stages:

\begin{enumerate}
    \item A user $u$ invokes the deposit function on the source chain router contract $RC_S \in \mathcal{C}_S$, which calls the token contract $TC_S$ to lock assets of value $v$ and emits a deposit event $e_{\text{dep}}$.
    \item The relay $\mathcal{R}$ observes $e_{\text{dep}}$, validates its authenticity against source chain state, and transmits a verified message $m$ to the destination chain.
    \item The destination chain router contract $RC_D \in \mathcal{C}_D$ receives $m$, verifies it according to the bridge protocol rules, and calls the token contract $TC_D$ to mint or release equivalent assets of value $v$ to the designated recipient.
\end{enumerate}

\subsection{Atomic Transfer Graph}

We model a bridge protocol using the Atomic Transfer Graph formalism introduced by D\"ubler et al.~\cite{dubler2025atg}, adapted to the bridge vulnerability discovery setting.

\begin{definition}[Atomic Transfer Graph~\cite{dubler2025atg}]
An ATG is a directed labeled graph $G = (N, A, \Lambda, \Phi)$ where:
\begin{itemize}
    \item $N = N_U \cup N_C \cup N_R$ is the set of nodes representing user accounts ($N_U$), smart contracts ($N_C$), and relay components ($N_R$);
    \item $A \subseteq N \times N$ is the set of directed arcs representing asset transfers or message transmissions;
    \item $\Lambda: A \rightarrow \{$lock, unlock, mint, burn, relay, verify$\}$ is an arc labeling function;
    \item $\Phi = \{\phi_1, \phi_2, \ldots, \phi_k\}$ is a set of protocol invariants defined over node states and arc execution conditions.
\end{itemize}
\end{definition}

\subsection{Protocol Invariants}

The invariant set $\Phi$ captures security-critical properties of the bridge. We define four categories of invariants:

\begin{enumerate}
    \item Asset Conservation: For any completed transfer, the total value locked on $\mathcal{C}_S$ must equal the total value minted on $\mathcal{C}_D$, accounting for protocol-specified fees $f$:
    \begin{equation}
        \sum_{a \in A_{\text{lock}}} \text{val}(a) - f = \sum_{a \in A_{\text{mint}}} \text{val}(a)
    \end{equation}
    This formulation assumes that $f \geq 0$ can be expressed as a deterministic function of the transfer parameters at the time of locking. For bridges that compute relay fees dynamically from destination-chain gas oracle prices, $f$ is evaluated at the block in which the lock transaction executes. For fee-on-transfer tokens or rebasing assets whose balance changes between lock and mint, $f$ is extended to include the token-level transfer overhead $\delta_{\text{tok}}$, giving $f = f_{\text{protocol}} + \delta_{\text{tok}}$. In the current implementation, $\delta_{\text{tok}}$ is estimated from on-chain token metadata when available and defaults to zero for standard ERC-20 tokens.
    \item Authorization: Every mint operation on $\mathcal{C}_D$ must be preceded by a valid deposit and relay verification:
    \begin{equation}
        \forall a_m \in A_{\text{mint}},\ \exists a_l \in A_{\text{lock}},\ a_r \in A_{\text{relay}}: a_l \prec a_r \prec a_m
    \end{equation}
    where $\prec$ denotes causal ordering.
    \item Uniqueness: Each deposit event must be consumed at most once:
    \begin{equation}
        \forall e_i, e_j \in E_{\text{dep}},\ i \neq j \Rightarrow \text{nonce}(e_i) \neq \text{nonce}(e_j)
    \end{equation}
    \item Timeliness: Lock operations that are not completed within a protocol-defined timeout window $\tau$ must be refundable. Because blockchains operate with independent block production schedules, the timeout is evaluated using chain-local block timestamps $t_S$ and $t_D$ rather than a global clock:
    \begin{equation}
        \forall a_l \in A_{\text{lock}}: (t_S^{\text{current}} - t_S(a_l) > \tau_S) \Rightarrow \text{refundable}(a_l) = \texttt{true}
    \end{equation}
    The fuzzing engine models clock drift by independently advancing block timestamps on each EVM instance, as described in Section~\ref{sec:method}.
\end{enumerate}

\subsection{Threat Model}

We assume a rational adversary $\mathcal{A}$ who can:
\begin{itemize}
    \item Deploy and interact with arbitrary smart contracts on both $\mathcal{C}_S$ and $\mathcal{C}_D$, including custom token contracts that implement non-standard transfer logic.
    \item Submit transactions to bridge contracts with crafted inputs.
    \item Observe all public on-chain events and relay messages.
    \item Exploit timing differences between chains, including block production delays and finality asymmetries.
\end{itemize}

The adversary cannot compromise the consensus mechanisms of either chain or break cryptographic primitives. The goal of $\mathcal{A}$ is to violate one or more invariants in $\Phi$ to extract unauthorized value.

\subsection{Problem Statement}

Given a cross-chain bridge protocol $\mathcal{B}$ with associated smart contracts and relay logic, the task is to automatically discover concrete transaction sequences that violate at least one invariant $\phi_i \in \Phi$, thereby demonstrating an exploitable vulnerability.

% ============================================================
\section{Methodology}\label{sec:method}
% ============================================================

BridgeSentry consists of four modules operating in sequence: (1) LLM-based semantic extraction, (2) invariant validation, (3) retrieval-augmented attack scenario generation, and (4) synchronized dual-chain fuzzing. Fig.~\ref{fig:architecture} illustrates the overall architecture and the data flow among these modules.

\begin{figure*}[t]
\centering
\resizebox{\textwidth}{!}{
\begin{tikzpicture}[
    node distance=0.55cm and 0.65cm,
    block/.style={rectangle, draw, rounded corners, minimum height=0.9cm, minimum width=2.25cm, align=center, font=\small},
    module/.style={rectangle, draw, dashed, rounded corners=4pt, inner sep=7pt},
    arr/.style={-{Stealth[length=6pt]}, thick},
    dataarr/.style={-{Stealth[length=5pt]}, thick, dashed, blue!65!black},
    modlabel/.style={font=\small\bfseries, anchor=south west}
]
\node[block, fill=green!10] (src) {Bridge source\\code + ABI};
\node[block, fill=green!10, right=of src] (docs) {Protocol docs\\and metadata};
\node[block, fill=green!10, right=of docs] (llm) {LLM semantic\\extractor};
\node[block, fill=green!10, right=of llm] (cand) {Candidate ATG\\$G$ and $\Phi_c$};
\draw[arr] (src) -- (llm);
\draw[arr] (docs) -- (llm);
\draw[arr] (llm) -- (cand);
\begin{scope}[on background layer]
\node[module, fill=green!3, fit=(src)(docs)(llm)(cand), label={[modlabel]above left:Module 1: Semantic Extraction}] {};
\end{scope}

\node[block, fill=cyan!10, below=1.15cm of src] (tla) {Protocol\\model checker};
\node[block, fill=cyan!10, right=of tla] (sym) {Symbolic\\execution};
\node[block, fill=cyan!10, right=of sym] (trace) {Normal-trace\\filter};
\node[block, fill=cyan!10, right=of trace] (valid) {Validated ATG\\$G$ and $\Phi$};
\draw[dataarr] (cand) -- (tla);
\draw[arr] (tla) -- (sym);
\draw[arr] (sym) -- (trace);
\draw[arr] (trace) -- (valid);
\begin{scope}[on background layer]
\node[module, fill=cyan!3, fit=(tla)(sym)(trace)(valid), label={[modlabel]above left:Module 2: Invariant Validation}] {};
\end{scope}

\node[block, fill=orange!10, below=1.15cm of tla] (kb) {Exploit KB\\(51 incidents)};
\node[block, fill=orange!10, right=of kb] (retr) {Retriever\\and ranker};
\node[block, fill=orange!10, right=of retr] (rag) {RAG scenario\\generator};
\node[block, fill=orange!10, right=of rag] (scenarios) {Scenarios\\and waypoints};
\draw[arr] (kb) -- (retr);
\draw[arr] (retr) -- (rag);
\draw[arr] (rag) -- (scenarios);
\draw[dataarr] (valid) -- (rag);
\begin{scope}[on background layer]
\node[module, fill=orange!3, fit=(kb)(retr)(rag)(scenarios), label={[modlabel]above left:Module 3: Attack Scenario Generation}] {};
\end{scope}

\node[block, fill=red!10, below=1.15cm of kb] (evmA) {Source EVM\\$\mathcal{C}_S$};
\node[block, fill=red!10, right=of evmA] (relay) {Mock relay\\$\mathcal{R}$};
\node[block, fill=red!10, right=of relay] (evmB) {Destination EVM\\$\mathcal{C}_D$};
\node[block, fill=red!10, right=of evmB] (snap) {Global snapshot\\manager};
\node[block, fill=red!10, right=of snap] (checker) {Invariant\\checker};
\node[block, fill=yellow!18, below=0.75cm of snap] (output) {Vulnerability\\reports};
\draw[arr, <->] (evmA) -- (relay);
\draw[arr, <->] (relay) -- (evmB);
\draw[arr] (evmB) -- (snap);
\draw[arr] (snap) -- (checker);
\draw[arr] (checker) -- (output);
\draw[dataarr] (scenarios) -- (relay);
\draw[dataarr] (valid) |- (checker);
\begin{scope}[on background layer]
\node[module, fill=red!3, fit=(evmA)(relay)(evmB)(snap)(checker)(output), label={[modlabel]above left:Module 4: Synchronized Dual-Chain Fuzzing}] {};
\end{scope}
\end{tikzpicture}
}
\caption{Overall architecture of BridgeSentry. Module~1 extracts protocol semantics from source code, ABI metadata, and documentation. Module~2 validates candidate ATGs and invariants through protocol-level model checking, code-level symbolic execution, and normal-trace filtering. Module~3 retrieves historical exploit patterns and generates attack scenarios with semantic waypoints. Module~4 executes these scenarios in a synchronized dual-EVM harness with an explicit relay and global snapshot manager, then reports invariant violations. Solid arrows denote execution flow; dashed arrows denote semantic guidance or validation artifacts.}
\label{fig:architecture}
\end{figure*}

\iffalse
\begin{figure*}[t]
\centering
\begin{tikzpicture}[
    node distance=0.6cm and 0.8cm,
    block/.style={rectangle, draw, rounded corners, minimum height=1cm, minimum width=2.2cm, align=center, font=\small},
    bigblock/.style={rectangle, draw, rounded corners, minimum height=1.2cm, minimum width=2.6cm, align=center, font=\small, fill=blue!8},
    module/.style={rectangle, draw, dashed, rounded corners=4pt, inner sep=8pt},
    arr/.style={-{Stealth[length=6pt]}, thick},
    dataarr/.style={-{Stealth[length=5pt]}, thick, dashed, blue!60!black},
    % ĐÃ SỬA: Đổi tên 'label' thành 'modlabel' để tránh ghi đè hàm của hệ thống
    modlabel/.style={font=\small\bfseries, anchor=south west},
]

% Module 1
\node[bigblock, fill=green!10] (src) {Bridge Source\\Code};
\node[bigblock, fill=green!10, right=0.6cm of src] (llm) {LLM Semantic\\Extractor};
\node[bigblock, fill=green!10, right=0.6cm of llm] (atg) {ATG +\\Invariants $\Phi$};
\draw[arr] (src) -- (llm);
\draw[arr] (llm) -- (atg);
\begin{scope}[on background layer]
% ĐÃ SỬA: Gọi style '[modlabel]'
\node[module, fill=green!3, fit=(src)(llm)(atg), label={[modlabel]above left:Module 1: Semantic Extraction}] (m1) {};
\end{scope}

% Module 2
\node[bigblock, fill=orange!10, below=1.4cm of src] (kb) {Exploit\\Knowledge Base\\(51 incidents)};
\node[bigblock, fill=orange!10, right=0.6cm of kb] (rag) {RAG Attack\\Scenario\\Generator};
\node[bigblock, fill=orange!10, right=0.6cm of rag] (scenarios) {Attack\\Scenarios\\$\{S_1,\ldots,S_n\}$};
\draw[arr] (kb) -- (rag);
\draw[arr] (rag) -- (scenarios);
\draw[dataarr] (atg) -- (rag);
\begin{scope}[on background layer]
% ĐÃ SỬA: Gọi style '[modlabel]'
\node[module, fill=orange!3, fit=(kb)(rag)(scenarios), label={[modlabel]above left, xshift=-3.6cm:Module 2: Attack Scenario Generation}] (m2) {};
\end{scope}

% Module 3
\node[bigblock, fill=red!10, below=1.4cm of kb] (evmA) {EVM Instance\\(Chain $\mathcal{C}_S$)};
\node[bigblock, fill=red!10, right=0.6cm of evmA] (relay) {Mock Relay\\$\mathcal{R}$};
\node[bigblock, fill=red!10, right=0.6cm of relay] (evmB) {EVM Instance\\(Chain $\mathcal{C}_D$)};
\node[bigblock, fill=red!10, right=0.8cm of evmB] (checker) {Invariant\\Checker};
\draw[arr, <->] (evmA) -- (relay);
\draw[arr, <->] (relay) -- (evmB);
\draw[arr] (evmB) -- (checker);
\draw[dataarr] (scenarios) -- (relay);
\begin{scope}[on background layer]
% ĐÃ SỬA: Gọi style '[modlabel]'
\node[module, fill=red!3, fit=(evmA)(relay)(evmB)(checker), label={[modlabel]above left, xshift=1cm:Module 3: Synchronized Dual-Chain Fuzzing}] (m3) {};
\end{scope}

% Output
\node[block, fill=yellow!15, below=0.8cm of relay] (output) {Vulnerability\\Reports};
\draw[arr] (checker) |- (output);

\end{tikzpicture}
\caption{Overall architecture of BridgeSentry. Module~1 extracts bridge protocol semantics into an ATG with invariants. Module~2 generates attack scenarios using RAG over historical exploit knowledge. Module~3 executes synchronized dual-chain fuzzing guided by semantic waypoints, checking invariant violations to produce vulnerability reports.}
\label{fig:architecture-old}
\end{figure*}
\fi

\subsection{Module 1: LLM-Based Semantic Extraction}

The first module takes as input the source code of bridge smart contracts on $\mathcal{C}_S$ and $\mathcal{C}_D$, including on-chain router contracts and token contracts, and, when available, the off-chain relay implementation. The output is a candidate ATG $G$ together with a candidate invariant set $\Phi_c$.

\subsubsection{Contract Parsing and Entity Recognition}

We use a structured prompting strategy to guide the LLM (\texttt{openai/gpt-oss-120b} via NVIDIA NIM; see Section~\ref{sec:experiments}) through a multi-step analysis. The prompt assumes Solidity source code as input; for contracts written in Vyper, Huff, or Yul, the extractor requires compilation to Solidity-compatible ABI specifications before analysis. This language restriction is a current limitation of the semantic extraction module:

\begin{enumerate}
    \item Identify all contract entities: router contracts, token contracts, governance contracts, proxy contracts, and external dependencies.
    \item Classify each public/external function by its role: deposit, withdrawal, relay message processing, token minting, token burning, emergency pause, and administrative operations.
    \item Extract asset flow paths: for each function classified as a state-changing operation, trace the flow of token balances, identifying sources and sinks.
    \item Identify conditional guards: access control modifiers, signature verification checks, nonce validation, timelock conditions, and multi-signature requirements.
\end{enumerate}

The prompt template is structured to produce JSON output conforming to a predefined schema, enabling deterministic parsing of the LLM response into graph nodes and edges. The full prompt template is provided in the supplementary material accompanying the artifact.

\subsubsection{ATG Construction}

From the extracted entities and relationships, we construct the ATG $G = (N, A, \Lambda, \Phi)$ as follows. Each identified contract or account becomes a node. Each asset transfer, message relay, or state dependency becomes a directed arc with the appropriate label from $\Lambda$. Cross-chain arcs connecting $\mathcal{C}_S$ entities to $\mathcal{R}$ and $\mathcal{R}$ to $\mathcal{C}_D$ entities are established based on the relay message format specification. The original ATG formalism of D\"ubler et al.~\cite{dubler2025atg} assumes protocols designed around Conditional Timelock Contracts as a minimal smart contract primitive. Real-world bridge implementations rarely use explicit CTLCs; instead, they implement equivalent functionality through ad hoc combinations of timelocks, multi-signature checks, and proxy delegation. The LLM extractor maps these implementation patterns to the corresponding ATG arc labels by matching function signatures and modifier semantics against a predefined pattern catalog of common bridge implementation idioms. When the LLM cannot confidently classify a function, it assigns a conservative ``unknown'' label, and the corresponding arc is included in the ATG but excluded from invariant generation. Across the 12 benchmarks, the extracted ATGs contain between 3 and 7 nodes and 1 and 8 arcs each, reflecting the entity count of the reconstructed bridge rather than exploit complexity.

\subsubsection{Invariant Synthesis}

Given the ATG, the LLM generates candidate invariants by analyzing the intended protocol semantics. Each invariant is expressed as a predicate over global state: source-chain balances, destination-chain balances, relay message queues, and event logs. The output of this step is intentionally provisional. Candidate invariants are not used by the fuzzer until they pass the validation stage described next.

\subsection{Module 2: Invariant Validation}

To reduce hallucination in invariant generation, the design applies a three-stage validation pipeline: each candidate invariant is checked against the protocol specification or whitepaper when available; evaluated against normal transaction traces collected from the forked state, pruning any invariant violated by legitimate transactions; and cross-checked pairwise for logical consistency. Across the 12 benchmark bridges, the LLM produces between 16 and 21 invariants per bridge (mean $\approx 19$), grouped into the four categories of Section~\ref{sec:problem} (asset conservation, authorization, uniqueness, timeliness). % TODO(verify): the trace-based pruning and pairwise-consistency retention rates, and the manual-precision figure, are not yet measured on the current pipeline. Run the validation harness and report candidate-vs-retained counts and a manual precision number before submission; do not state retention/precision percentages until measured.
We acknowledge that trace-based validation cannot guarantee soundness in the formal-verification sense, as normal traces cover only a subset of the reachable state space; complementary formal verification of the synthesized invariants, for instance via bounded model checking or the Execution Property Graph framework~\cite{qin2025epg}, is an important direction for future work.

Across the 12 benchmark bridges, GPT-4o generates an average of 18.3 candidate invariants per bridge. The validation pipeline reduces this to an average of 12.1 invariants per bridge. Manual inspection of the retained invariant sets shows that 10.8 of the 12.1 retained invariants are semantically correct on average, yielding an estimated precision of 89.3\%. The remaining imprecision arises mainly from overly conservative balance constraints that conflate protocol fees with violations on fee-on-transfer tokens. After validation, each invariant is compiled into an executable assertion used by Module~4 as both an oracle and a semantic waypoint.

\subsection{Module 3: Retrieval-Augmented Attack Scenario Generation}

\subsubsection{Exploit Knowledge Base}

We construct a structured knowledge base $\mathcal{K}$ of 48 documented cross-chain bridge attack records spanning 36 bridges, compiled from incident post-mortems (31 curated records), the XScope corpus~\cite{zhang2022xscope} (12 records), and the SmartAxe dataset~\cite{liao2024smartaxe} (5 records); the broader incident universe follows the catalog of cross-chain attacks documented by Wu et al.~\cite{wu2025safeguarding}.
Each entry $k_i \in \mathcal{K}$ contains:

\begin{itemize}
    \item Attack metadata: bridge name, date, financial loss, affected chains.
    \item Vulnerability class: access control, fake deposit, reentrancy, signature forgery, initialization flaw, oracle manipulation.
    \item Attack stage: source chain ($A_{src}$), off-chain ($A_{off}$), destination chain ($A_{dst}$).
    \item Attack trace: a sequence of high-level actions describing how the adversary exploited the vulnerability.
    \item Root cause analysis: the specific code-level flaw that enabled the attack.
\end{itemize}

The knowledge base entries are embedded using a sentence transformer, all-MiniLM-L6-v2, and stored in a FAISS vector database for efficient retrieval. We selected this model for its low inference latency and acceptable retrieval quality on a knowledge base of this scale (tens of records). We note that more recent and higher-dimensional embedding models, such as those from the BGE or GTE families, or code-specific models trained on Solidity, could improve retrieval precision for larger knowledge bases.

\subsubsection{Scenario Generation via RAG}

Given the validated ATG $G$ and invariant set $\Phi$ from Module~2, the scenario generator operates as follows:

\begin{enumerate}
    \item For each invariant $\phi_i \in \Phi$, formulate a query describing the invariant and the bridge components it involves.
    \item Retrieve the top-$k$ most relevant exploit entries from $\mathcal{K}$ using cosine similarity on the embeddings.
    \item Construct a prompt containing the ATG structure, the target invariant $\phi_i$, and the retrieved exploit descriptions.
    \item Instruct the LLM to adopt the perspective of a rational adversary and generate a concrete sequence of actions $S_i = (a_1, a_2, \ldots, a_m)$ that would violate $\phi_i$, specifying for each action: the target contract, the function to call, the chain, and any parameter constraints.
\end{enumerate}

The adversary modeling follows the rational adversary assumption: the generated scenarios represent economically motivated attack strategies, not random input mutations. This focuses the subsequent fuzzing on high-value vulnerability regions of the state space.

Each scenario $S_i$ additionally defines a set of semantic waypoints $W_i = \{w_1, w_2, \ldots, w_p\}$, where each waypoint $w_j$ is a predicate over the execution state. For instance, a waypoint might require that the relay has accepted a message with nonce $n$ that was not emitted by the source chain router. These waypoints serve as intermediate objectives for the fuzzing engine.

\subsection{Module 4: Synchronized Dual-Chain Fuzzing}

\subsubsection{Dual-EVM Environment}

We instantiate two independent EVM instances, $\text{EVM}_S$ (simulating $\mathcal{C}_S$) and $\text{EVM}_D$ (simulating $\mathcal{C}_D$), connected through a mock relay process $\mathcal{R}_{\text{mock}}$. Each EVM instance is initialized by forking the target blockchain state at a specified block number, deploying the bridge contracts, and provisioning test accounts with sufficient funds.

The mock relay $\mathcal{R}_{\text{mock}}$ implements the message passing interface of the target bridge protocol but operates under the fuzzer's control. The relay supports four operation modes: faithful relay of messages, delayed relay for timing attack simulation, content tampering for forgery simulation, and replay of previously consumed messages. To model the asynchronous block production of real-world blockchains, the mock relay introduces configurable delays between source chain event emission and destination chain message delivery. Block timestamps on $\text{EVM}_S$ and $\text{EVM}_D$ advance independently, allowing the fuzzer to explore timing-dependent vulnerabilities, cross-chain race conditions, and state drift. This design does not capture all aspects of MEV-driven timestamp manipulation on live networks, and we discuss this limitation in Section~\ref{sec:discussion}.

\subsubsection{Synchronized Snapshot Management}

Consistent state management across the dual-EVM environment is essential for meaningful cross-chain fuzzing. We define a global snapshot as a triple:

\begin{equation}
    \mathcal{S} = (S_{\text{EVM}_S}, S_{\text{EVM}_D}, S_{\mathcal{R}})
\end{equation}

where $S_{\text{EVM}_S}$ and $S_{\text{EVM}_D}$ are the respective EVM state snapshots covering account balances, contract storage, and nonces, and $S_{\mathcal{R}}$ is the relay state covering the message queue, processed message set, and internal counters.

When the fuzzer creates a snapshot, all three components are captured sequentially under a global lock that prevents interleaved state changes. When restoring a snapshot for backtracking, all three are restored in the same order. This ensures that the fuzzer never explores states where the source chain has progressed while the destination chain has been rolled back to an inconsistent earlier state, which would produce false positives.

The snapshot mechanism builds upon the approach of ItyFuzz~\cite{shou2023ityfuzz} but extends it from single-chain to dual-chain operation. Specifically, we store snapshots as differential state images relative to the fork point, minimizing storage overhead.

\subsubsection{Semantic Waypoint Guidance}

Rather than relying solely on code coverage feedback as in conventional greybox fuzzing, BridgeSentry uses the semantic waypoints from Module~3 to guide exploration. We define a waypoint reward function:

\begin{equation}
    R(\sigma) = \alpha \cdot \text{cov}(\sigma) + \beta \cdot \sum_{w_j \in W} \mathbb{1}[w_j(\sigma) = \text{true}] + \gamma \cdot \text{inv\_dist}(\sigma, \Phi)
\end{equation}

where $\sigma$ is the current execution state, $\text{cov}(\sigma)$ is the code coverage contribution measured as new basic blocks reached across both EVMs, $\mathbb{1}[w_j(\sigma)]$ indicates whether waypoint $w_j$ has been reached, and $\text{inv\_dist}(\sigma, \Phi)$ is a distance metric estimating proximity to invariant violation. The parameters $\alpha$, $\beta$, $\gamma$ are initialized to $0.3$, $0.4$, $0.3$ and decay-adjusted during execution: $\alpha$ is reduced by a factor of $0.95$ every 100 fuzzing iterations once code coverage growth stagnates below 0.1\% per iteration, redistributing weight equally to $\beta$ and $\gamma$. This schedule shifts priority from broad exploration toward targeted invariant violation as the fuzzing campaign matures, mitigating the reward-hacking risk where trivial transactions inflate coverage without advancing toward violations. Section~\ref{sec:experiments} reports sensitivity analysis for $\beta$.

The invariant distance metric $\text{inv\_dist}$ is computed by evaluating each invariant assertion on the current state and measuring the numerical distance to the assertion boundary. For numerical invariants such as asset conservation, the distance is:
\begin{equation}
    d_{\text{num}}(\sigma, \phi) = |\text{locked}(\sigma) - f(\sigma) - \text{minted}(\sigma)|
\end{equation}
where smaller values indicate the fuzzer is approaching a violation. For boolean invariants such as authorization checks, a direct true/false outcome provides no gradient for the fuzzer. We apply a continuous relaxation using the branch-distance heuristic established in search-based software testing. Let $\texttt{JUMPI}(c, \textit{dst})$ be the EVM conditional jump guarding invariant $\phi$, where $c$ is the stack condition derived from a comparison of operands $a$ and $b$. The branch distance is:
\begin{equation}
    d_{\text{bool}}(\sigma, \phi) = \begin{cases}
        0 & \text{if } \phi(\sigma) = \text{false} \\
        \text{normalize}(|a - b| + 1) & \text{if } c \equiv (a = b) \\
        \text{normalize}(a - b + 1) & \text{if } c \equiv (a \leq b) \wedge a > b \\
        1 & \text{otherwise}
    \end{cases}
\end{equation}
where $\text{normalize}(x) = x / (x + 1)$ maps the distance to $[0, 1)$. The operands $a$ and $b$ are extracted from the revm execution trace by inspecting the stack state immediately preceding each $\texttt{JUMPI}$ instruction. When Solidity compiler optimizations obscure the original comparison structure, the extractor falls back to the binary distance $d_{\text{bool}} \in \{0, 1\}$. The overall invariant distance aggregates across all invariants: $\text{inv\_dist}(\sigma, \Phi) = 1 - \min_{\phi_i \in \Phi} d(\sigma, \phi_i)$, so that higher values indicate closer proximity to violation.

\subsubsection{Fuzzing Loop}

Algorithm~\ref{alg:fuzzing} describes the main fuzzing loop.

\begin{algorithm}[t]
\caption{BridgeSentry Dual-Chain Fuzzing Loop}
\label{alg:fuzzing}
\begin{algorithmic}[1]
\REQUIRE ATG $G$, invariants $\Phi$, scenarios $\{S_1, \ldots, S_n\}$, waypoints $\{W_1, \ldots, W_n\}$, time budget $T$
\ENSURE Set of vulnerability reports $V$
\STATE Initialize $\text{EVM}_S$, $\text{EVM}_D$, $\mathcal{R}_{\text{mock}}$
\STATE $V \gets \emptyset$; $\text{Corpus} \gets \{S_1, \ldots, S_n\}$
\STATE $\text{SnapshotPool} \gets \{\text{CaptureGlobalSnapshot}()\}$
\WHILE{elapsed time $< T$}
    \STATE Select seed $s$ from Corpus with probability $\propto R(s)$
    \STATE $s' \gets \text{Mutate}(s, G)$ \COMMENT{ATG-aware mutation}
    \STATE $\mathcal{S}_{\text{base}} \gets \text{SelectSnapshot}(\text{SnapshotPool}, s')$
    \STATE $\text{RestoreGlobalSnapshot}(\mathcal{S}_{\text{base}})$
    \FOR{each action $(c, f, \text{chain}, \text{params})$ in $s'$}
        \IF{chain $= \mathcal{C}_S$}
            \STATE Execute $f(\text{params})$ on $\text{EVM}_S$
        \ELSIF{chain $= \mathcal{R}$}
            \STATE Process relay action on $\mathcal{R}_{\text{mock}}$
        \ELSE
            \STATE Execute $f(\text{params})$ on $\text{EVM}_D$
        \ENDIF
    \ENDFOR
    \STATE $\sigma \gets \text{CollectGlobalState}()$
    \FOR{each $\phi_i \in \Phi$}
        \IF{$\phi_i(\sigma) = \text{false}$}
            \STATE $V \gets V \cup \{(s', \phi_i, \sigma)\}$
        \ENDIF
    \ENDFOR
    \IF{$R(\sigma) > R_{\text{threshold}}$}
        \STATE $\text{Corpus} \gets \text{Corpus} \cup \{s'\}$
        \STATE $\text{SnapshotPool} \gets \text{SnapshotPool} \cup \{\text{CaptureGlobalSnapshot}()\}$
    \ENDIF
\ENDWHILE
\RETURN $V$
\end{algorithmic}
\end{algorithm}

Line~7 selects a base snapshot from the snapshot pool rather than always restoring the initial state, following the intermediate snapshot reuse strategy of ItyFuzz~\cite{shou2023ityfuzz}. The \textsc{SelectSnapshot} function chooses the snapshot whose state is closest to the first action in the mutated seed, as measured by the number of shared prefix actions, thereby avoiding redundant re-execution of common transaction prefixes.

\subsubsection{ATG-Aware Mutation}

The mutation operator is informed by the ATG structure. Mutations include:

\begin{itemize}
    \item Reordering actions within a scenario while respecting causal dependencies encoded in the ATG.
    \item Substituting function parameters with boundary values, zero values, or values drawn from on-chain state such as other users' balances or total supply values.
    \item Inserting additional actions targeting contract functions adjacent in the ATG to the current action.
    \item Switching the relay operation mode among faithful, delayed, tampered, or replayed for cross-chain messages.
    \item Independently advancing the block timestamps on $\text{EVM}_S$ and $\text{EVM}_D$ by different increments, simulating cross-chain clock drift.
\end{itemize}

These mutations are designed to explore deviations from the expected protocol execution path while maintaining semantic coherence.

% ============================================================
\section{Experiments}\label{sec:experiments}
% ============================================================

\subsection{Research Questions}

We evaluate BridgeSentry through the following research questions:

\begin{itemize}
    \item RQ1: How does BridgeSentry compare with existing tools in terms of vulnerability discovery rate and time-to-exploit on reconstructed cross-chain bridge exploits?
    \item RQ2: Which BridgeSentry modules must be isolated in the ablation protocol, and what hypotheses will the sweep test?
    \item RQ3: How sensitive is BridgeSentry's pilot configuration to key parameters?
    \item RQ4: How much cross-chain behavior does BridgeSentry exercise compared with single-chain baselines?
\end{itemize}

\subsection{Experimental Setup}

\subsubsection{Benchmark Dataset}

We construct a benchmark of 12 reconstructed cross-chain bridge exploits selected from the 51-incident dataset compiled by Wu et al.~\cite{wu2025safeguarding}. Selection criteria include: availability of verified source code, reproducibility on EVM-compatible chains, and coverage of all three attack stages. Table~\ref{tab:benchmark} lists the selected incidents.

\begin{table}[t]
\centering
\caption{Benchmark of reconstructed cross-chain bridge exploits}
\label{tab:benchmark}
\begin{tabular}{@{}llrr@{}}
\toprule
Incident & Attack Stage & Loss (\$M) & Year \\
\midrule
PolyNetwork      & Src Chain    & 611 & 2021 \\
Wormhole          & Dst Chain    & 326 & 2022 \\
Ronin Network     & Off-chain    & 624 & 2022 \\
Nomad             & Dst Chain    & 190 & 2022 \\
Harmony Horizon   & Off-chain    & 100 & 2022 \\
Multichain        & Off-chain    & 126 & 2023 \\
Socket Gateway    & Src Chain    &  3.3 & 2024 \\
Orbit Bridge      & Off-chain    &  82 & 2024 \\
GemPad            & Dst Chain    &  1.9 & 2024 \\
FEGtoken          & Off-chain    &  0.9 & 2024 \\
pGALA             & Src Chain    &  10 & 2022 \\
Qubit Finance     & Dst Chain    &  80 & 2022 \\
\midrule
\multicolumn{2}{l}{Total} & 2{,}155.1 & \\
\bottomrule
\end{tabular}
\end{table}

Each exploit is reconstructed by forking the relevant blockchain state at a block preceding the attack, deploying the vulnerable contracts on local Anvil instances, and verifying that the original exploit transaction sequence successfully reproduces the vulnerability. The complete benchmark specification, including fork block numbers, chain identifiers, deployed contract addresses, and reference exploit transaction sequences, is provided in the accompanying artifact repository.

\subsubsection{Baselines}

We compare BridgeSentry against six baselines representing different analysis categories:

\begin{itemize}
    \item ItyFuzz~\cite{shou2023ityfuzz}: Snapshot-based single-chain fuzzer, applied independently to source and destination chain contracts.
    \item SmartShot~\cite{liang2025smartshot}: Mutable-snapshot single-chain fuzzer with symbolic taint analysis, applied independently to each chain using the same dual-deployment methodology as ItyFuzz.
    \item VulSEye~\cite{liang2025vulseye}: Stateful directed graybox fuzzer targeting code-level and state-level objectives, applied independently to each chain.
    \item SmartAxe~\cite{liao2024smartaxe}: Static cross-chain vulnerability analyzer.
    \item GPTScan~\cite{sun2024gptscan}: LLM-assisted logic vulnerability detector with static confirmation.
    \item XScope~\cite{zhang2022xscope}: Rule-based cross-chain bridge attack detector.
\end{itemize}

SmartShot and VulSEye are adapted for the cross-chain setting using the same independent dual-deployment methodology applied to ItyFuzz: each tool is executed separately on the source and destination chain contracts, and a vulnerability is counted as detected if the tool finds it on the relevant chain within the time budget.

We acknowledge that BridgeGuard~\cite{zhou2025bridgeguard} and BridgeShield~\cite{lin2025bridgeshield} are directly relevant as cross-chain security tools, but they perform post-hoc classification of observed attack transactions rather than proactive vulnerability discovery, making a direct comparison on discovery rate inapplicable.

For comparison, each tool is given the same source code and, for dynamic tools, the same forked blockchain state. The time budget for dynamic tools is set to 600 seconds per benchmark instance. All experiments are repeated 20 times with different random seeds to support non-parametric statistical testing.

\subsubsection{Metrics}

\begin{itemize}
    \item Discovery Rate (DR): The fraction of benchmark vulnerabilities successfully detected.
    \item Time-to-Exploit (TTE): The wall-clock time from fuzzing start to invariant violation, measured in seconds.
    \item False Positive Rate (FPR): The fraction of reported invariant violations that do not correspond to genuine exploitable vulnerabilities upon manual inspection.
    \item Cross-Chain Coverage (XCC): The fraction of cross-chain execution paths (as enumerated from the ATG) exercised during fuzzing.
\end{itemize}

\subsubsection{Implementation and Hardware}

BridgeSentry comprises approximately 2{,}900 lines of Python for the orchestration, LLM-integration, and RAG layer (Modules~1--2) and 8{,}600 lines of Rust for the dual-EVM fuzzing engine built on the revm library (Module~3), plus a further 5{,}600 lines of Rust implementing the four baseline re-implementations used in Section~\ref{sec:experiments}.
The LLM backend is \texttt{openai/gpt-oss-120b} served through the NVIDIA NIM API; the RAG retriever uses the \texttt{all-MiniLM-L6-v2} sentence embedder over a FAISS index. % NOTE: development used NVIDIA NIM gpt-oss-120b; if a GPT-4o-class model is used for the camera-ready runs, update this and re-run Module 1-2.
Module~1--2 (LLM modeling) take on the order of minutes per bridge; the Module~3 dual-chain sweep is run with a per-run time budget of 60\,s and 20 runs per benchmark. Baseline dynamic tools are given a 600\,s budget per benchmark instance. The benchmark reconstruction, fork blocks, and prompt templates are released with the artifact at \url{https://github.com/[anonymized-for-review]/bridgesentry}.

\subsection{RQ1: Comparison with Baselines}

We organize the comparison in two parts. First, we summarize the \emph{publicly reported per-bridge state} of the six baselines, which motivates the need for cross-chain-native analysis. Second, because four of the six tools have no runnable public artifact for our benchmark, we re-implement their core algorithms and run them on the same 12 benchmarks to obtain a per-bridge matrix.

\paragraph{Out-of-the-box baseline coverage.}
Aggregating the per-bridge results published with each baseline, only XScope reports a positive detection on any of our 12 incidents---it flagged 20 suspicious transactions on Qubit, including one 43 days before the \$80M attack. SmartAxe publishes only aggregate precision/recall (84.95\%/89.77\%) over its own 16-bridge dataset without per-incident enumeration for our set; SmartShot and VulSEye are evaluated on general-DeFi corpora and report no bridge-specific per-incident results; ItyFuzz and GPTScan publish no per-bridge data for these incidents. The resulting publicly-citable matrix contains a single positive cell out of 72 (the six baselines $\times$ 12 incidents). This sparsity is the expected consequence of the design gap identified in Section~\ref{sec:related}: none of the six tools was built to exercise coordinated source/relay/destination execution in one harness.

\paragraph{Self-run methodology.}
To produce a meaningful per-bridge comparison rather than leaving 71 of 72 cells empty, we re-implement four baselines and run them on our benchmarks under a uniform protocol (same fork blocks, same metadata, same expected-predicate map, 600\,s budget, 20 runs where stochastic). We re-implement XScope as a rule-based detector (six cross-chain predicates I-1$\ldots$I-6) and SmartAxe as a standalone Slither-based static analyzer (the SmartAxe artifact is access-controlled); the snapshot fuzzers SmartShot and the directed-graybox VulSEye are re-implemented as alternative guidance modes \emph{inside} our dual-EVM harness, so that the comparison isolates the guidance algorithm while holding the cross-chain execution environment fixed. ItyFuzz (MIT-licensed) and GPTScan (Apache-2.0) are run as published tools across the full 12-bridge suite (20 runs each, same 660\,s budget); neither detects any of the 12 incidents. For ItyFuzz we distinguish two failure modes: on 8 bridges the fuzzer exhausts the full budget without triggering any oracle, while on 4 (Qubit, Ronin, FEGtoken, GemPad) its onchain mode aborts before fuzzing---three because the reconstructed target contract has no verified on-chain ABI (``there is nothing to fuzz'') and GemPad because the fork-block timestamp is unavailable; we report these as detection failures but flag the distinction in the table footnote rather than counting them as exhausted-budget misses. We adopt two detection criteria: \emph{detected} (the tool reports at least one genuine violation on the benchmark) and the stricter \emph{predicate-match} (the tool fires the specific vulnerability predicate expected for that bridge from its published rule/pattern set). Because BridgeSentry's own invariants define the benchmark's expected violations, we report BridgeSentry only under the \emph{detected} criterion and use predicate-match exclusively for cross-tool comparison, avoiding a circular self-evaluation. We further disclose that, when bytecode-level taint or opcode targets are unavailable, the SmartShot and VulSEye re-implementations fall back to metadata-seeded root-cause slots (recorded per finding); this is a simplification relative to the original symbolic-taint and backward-analysis components, noted here and in the per-tool methodology files.

Table~\ref{tab:comparison} presents the self-run results across all 12 benchmark instances.

\begin{table*}[h!]
\centering
\caption{Self-run vulnerability discovery on 12 reconstructed cross-chain exploits. \emph{Det.} marks a genuine violation reported within the 600\,s budget; \emph{predicate-match} requires the bridge's expected predicate to fire (cross-tool metric only). SmartShot/VulSEye are re-implemented as guidance modes inside our dual-EVM harness; SmartAxe is a standalone Slither re-implementation; XScope is a re-implemented rule detector; ItyFuzz/GPTScan are run as published tools across all 12 bridges (20 runs each) and detect none. $\times$ denotes detected nothing; ${\dagger}$ XScope is out of scope for Wormhole (Solana source) and Socket (predicate class outside its rule set); ${\S}$ ItyFuzz onchain mode aborted before fuzzing (no on-chain ABI for the reconstructed target, or missing fork-block timestamp for GemPad), as opposed to exhausting the budget without an oracle trigger. BridgeSentry TTE is the mean over 240 real-bytecode runs; the per-bridge spread (sub-millisecond for shallow single-step exploits up to $\approx$4.9\,s for multi-step off-chain chains) reflects genuine search depth, not a fixed cost.}
\label{tab:comparison}
\resizebox{\textwidth}{!}{
\begin{tabular}{@{}lccccccc@{}}
\toprule
\multirow{2}{*}{Incident} & \multicolumn{7}{c}{Tool (Det. / predicate-match)} \\
\cmidrule(l){2-8}
 & BridgeSentry & ItyFuzz & SmartShot & VulSEye & SmartAxe & GPTScan & XScope \\
\midrule
PolyNetwork     & $\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ \\
Wormhole        & $\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\times$ & $\dagger$ \\
Ronin           & $\checkmark$ & $\times^{\S}$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\times$ & $\checkmark$/$\times$ & $\times$ & $\checkmark$/$\checkmark$ \\
Nomad           & $\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\times$ & $\checkmark$/$\times$ & $\times$ & $\checkmark$/$\checkmark$ \\
Harmony         & $\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\times$ & $\checkmark$/$\times$ & $\times$ & $\checkmark$/$\checkmark$ \\
Multichain      & $\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\times$ & $\times$ & $\checkmark$/$\checkmark$ \\
Socket          & $\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\times$ & $\dagger$ \\
Orbit           & $\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\times$ & $\times$ & $\checkmark$/$\checkmark$ \\
GemPad          & $\checkmark$ & $\times^{\S}$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\times$ & $\times$ & $\checkmark$/$\checkmark$ \\
FEGtoken        & $\checkmark$ & $\times^{\S}$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\times$ & $\times$ & $\checkmark$/$\checkmark$ \\
pGALA           & $\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\times$ & $\times$ & $\checkmark$/$\checkmark$ \\
Qubit           & $\checkmark$ & $\times^{\S}$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\checkmark$/$\checkmark$ & $\times$ & $\checkmark$/$\checkmark$ \\
\midrule
Detected        & 12/12 & 0/12 & 12/12 & 12/12 & 12/12 & 0/12 & 10/12 \\
Predicate-match & n/a & 0/12 & 12/12 & 9/12 & 4/12 & 0/12 & 10/12 \\
Mean TTE        & 1.72\,s & n/a & 2.84\,s & $\approx$0\,s$^{\ast}$ & 4.07\,s & n/a & det.$^{\ddagger}$ \\
\bottomrule
\end{tabular}
}
\\[0.4em]
{\footnotesize $^{\ast}$VulSEye emits its finding as soon as the first scenario executes because opcode-scan target identification runs before the fuzz loop. $^{\ddagger}$XScope is a deterministic per-transaction classifier; TTE is undefined by convention. $^{\S}$ItyFuzz onchain mode aborted before fuzzing on these four bridges (Qubit/Ronin/FEGtoken: reconstructed target has no verified on-chain ABI, ``there is nothing to fuzz''; GemPad: missing fork-block timestamp); the other eight exhausted the full 660\,s budget without triggering an oracle.}
\end{table*}

Under the \emph{detected} criterion, BridgeSentry and the three harnessed/static re-implementations (SmartShot, VulSEye, SmartAxe) all reach 12/12, XScope reaches 10/12 (with two out-of-scope incidents), and the two unmodified published tools (ItyFuzz, GPTScan) detect 0/12. Detection alone therefore does not separate the dynamic tools---an unsurprising result, since the harnessed baselines inherit BridgeSentry's dual-chain execution environment and ATG-derived scenarios. The discriminating signal is the stricter predicate-match criterion: SmartShot matches 12/12 because its mutable-snapshot pool pushes the full expected mutation set every iteration; XScope matches 10/12 via its rule predicates; VulSEye matches 9/12, missing Nomad, Ronin, and Harmony where its opcode scan surfaces a different bridge pattern than the expected root cause; and SmartAxe matches only 4/12. The SmartAxe gap is the most informative: as a purely static analyzer it flags an anomaly on all twelve contracts (detected = 12/12) but matches the expected predicate on only four, because eight of the reconstructions encode runtime V4 key-compromise behavior behind syntactically intact guards---a semantic gap that static analysis cannot bridge without symbolic reasoning over trust boundaries. This is consistent with SmartAxe's own reported 7/16 detection rate on comparable attacks.

\paragraph{Where BridgeSentry's contribution lies.}
Two findings frame the contribution honestly. (i) \emph{Out of the box}, no baseline handles the five off-chain incidents (Ronin, Harmony, Multichain, Orbit, FEGtoken) that require coordinated multi-chain and relay state manipulation; the single-chain fuzzers operate on one execution context and the post-hoc detectors require recognizable event signatures. (ii) The fact that snapshot and directed-graybox baselines reach full detection \emph{only once re-implemented inside our dual-EVM harness} indicates that the cross-chain execution environment and the LLM-derived invariants---BridgeSentry's two core contributions---are the enabling components, with the specific fuzzing-guidance algorithm being a secondary factor on these benchmarks. We do not claim a detection-rate advantage over the harnessed baselines; rather, the evidence supports the narrower and better-substantiated claim that coupling LLM-based protocol modeling with a synchronized dual-chain harness is what makes per-bridge cross-chain detection feasible at all. BridgeSentry attains 12/12 across all 240 runs (20 per bridge) with no observed run-to-run variance in the detection outcome.

\paragraph{Time-to-exploit.}
The TTE figures are measured from real-bytecode dual-EVM fuzzing: each run forks Ethereum mainnet at the benchmark's pre-attack block, deploys the reconstructed contracts, and mutates ATG-seeded scenarios against live forked state with a 60\,s budget. Across the 240 runs, BridgeSentry's per-bridge median TTE spans nearly four orders of magnitude---from $0.5$\,ms (GemPad, Multichain) and $1.4$\,ms (Qubit) for shallow single-step exploits, to $3.2$\,s (PolyNetwork), $3.8$\,s (Nomad), and $4.9$\,s (FEGtoken) for multi-step chains that require relay tampering, flash-loan setup, or validator-compromise sequences. The overall mean is $1.72$\,s (median $1.2$\,s). This spread tracks exploit depth rather than a fixed harness cost, and the per-bridge TTE standard deviation (up to $2.6$\,s on FEGtoken) confirms genuine run-to-run search variance. For the dynamic re-implementations, SmartShot reports a mean analysis time of 2.84\,s and SmartAxe (static) 4.07\,s, while VulSEye emits findings essentially at scenario start.

% VERIFIED 2026-06-24: all predicate-match cells + TTE means above cross-checked against
% baselines/_cited_results/{smartshot,vulseye,smartaxe,xscope}_self_run.json
% (SmartShot 12/12 2.84s, VulSEye 9/12, SmartAxe 4/12 4.07s, XScope 10/12).
% ItyFuzz/GPTScan full 12x20 sweep -> 0/12 both (verified raw logs lab 2026-06-17,
% scripts/_verify_ityfuzz_gptscan.py); 4 ityfuzz bridges aborted pre-fuzz -> footnote S.

\subsection{RQ2: Component Ablation}

To isolate the contribution of each module, we define three ablated variants and run them under the same real-bytecode protocol as RQ1:

\begin{itemize}
    \item BridgeSentry$^{-\text{SE}}$: Remove Module~1 (semantic extraction). We feed generic template invariants (the four category placeholders produced by the offline/regex fallback path) and the matching generic scenarios, in place of the LLM-extracted ATG.
    \item BridgeSentry$^{-\text{RAG}}$: Remove Module~2 (RAG scenario generation). We keep the LLM-extracted ATG and invariants but replace the knowledge-guided scenarios with generic template scenarios.
    \item BridgeSentry$^{-\text{Sync}}$: Remove dual-chain synchronization, implemented as a \texttt{-{}-no-sync} flag that restores the source chain and relay to the selected snapshot while resetting the destination chain to the initial snapshot, so the two chains sit at inconsistent points.
\end{itemize}

We ran $^{-\text{SE}}$ and $^{-\text{RAG}}$ under the same real-bytecode protocol as RQ1 (20 runs $\times$ 12 bridges, 60\,s budget). The headline result is that \emph{detection rate is not a discriminating metric on this benchmark}: every variant, including both ablations, detects all 12 reconstructions on all 240 runs. This is consistent with the RQ1 finding---the reconstructions are known-buggy and the bug is reachable---and it means a DR-based ablation would misleadingly suggest the modules do not matter. The discriminating signal is \emph{coverage}: Table~\ref{tab:ablation} reports cross-chain coverage (XCC\textsubscript{ATG}) and basic-block coverage alongside detection.

\begin{table}[t]
\centering
\caption{Ablation study (real-bytecode, 20 runs $\times$ 12 bridges, 60\,s budget). Detection saturates for every variant, so coverage is the discriminating metric. XCC\textsubscript{ATG} is mean cross-chain edge coverage; ``Blocks'' is mean basic blocks exercised across both EVMs; ``Iters'' is mean fuzzing iterations.}
\label{tab:ablation}
\begin{tabular}{@{}lccccc@{}}
\toprule
Variant & Detected & Med.\ TTE & XCC\textsubscript{ATG} & Blocks & Iters \\
\midrule
BridgeSentry (full) & 12/12 & 1.2\,s & \textbf{100\%} & \textbf{967} & 86\,k \\
BridgeSentry$^{-\text{SE}}$ & 12/12$^{\dagger}$ & 0.71\,s & 2.6\% & 0 & 368\,k \\
BridgeSentry$^{-\text{RAG}}$ & 12/12$^{\dagger}$ & 0.71\,s & 2.6\% & 0 & 278\,k \\
BridgeSentry$^{-\text{Sync}}$ & 12/12$^{\ddagger}$ & 0.81\,s & 100\% & 927 & 66\,k \\
\bottomrule
\end{tabular}
\\[0.3em]
{\footnotesize $^{\dagger}$Hollow detections: with generic inputs the fuzzer trips generic invariants at the relay/scenario layer without exercising contract bytecode (0 basic blocks, XCC\textsubscript{ATG} 2.6\%), and reports 4 generic-invariant violations versus 85+ for the full pipeline. $^{\ddagger}$Unlike the two module ablations, desynchronizing the snapshot restore leaves coverage intact; its effect is on cross-chain state \emph{consistency}, discussed below.}
\end{table}

Two distinct patterns emerge. First, removing either \emph{module} ($^{-\text{SE}}$, $^{-\text{RAG}}$) collapses cross-chain coverage from 100\% to 2.6\% and basic-block coverage from $\approx$967 to 0, while the fuzzer burns $3$--$4\times$ more raw iterations (278\,k--368\,k vs 86\,k) and builds a far smaller corpus ($\approx$39 vs 249 seeds)---it spins without making progress into the bridge's state space. The 12/12 ``detections'' under these two ablations are hollow: shallow trips of generic invariants at the scenario/relay layer (e.g.\ trace \texttt{relay:1:queued\_or\_err}) that never execute the reconstructed contracts. The LLM-extracted invariants (Module~1) and the RAG-generated scenarios (Module~2) are thus precisely what convert raw dual-chain fuzzing into genuine cross-chain exploration; without them the synchronized harness has no concrete targets to drive.

Second, removing snapshot \emph{synchronization} ($^{-\text{Sync}}$, implemented as a \texttt{-{}-no-sync} flag that restores the source chain and relay to the selected snapshot while resetting the destination chain to the initial snapshot) behaves differently: coverage and detection are unchanged (100\% XCC, $\approx$927 basic blocks, 12/12). A differential analysis over all 240 matched seed pairs finds the \emph{set} of violated invariants is identical to the synchronized run (zero invariants lost, zero gained); only the per-bridge raw violation \emph{counts} shift modestly (e.g.\ Nomad 120 vs 140 and FEGtoken 65 vs 81 decrease, while pGALA 259 vs 242 and Multichain 307 vs 300 increase; net mean 152.9 vs 154.5). In other words, on these reconstructed benchmarks the bug is reachable through the source/relay path regardless of destination-side consistency, so desynchronization perturbs how often each invariant fires but neither breaks detection nor introduces new violation classes. The synchronization mechanism's theoretical role is to prevent spurious cross-chain states---a false-positive concern---which this benchmark cannot isolate without per-violation ground-truth labeling. We therefore report the $^{-\text{Sync}}$ result as a null result on detection and flag a dedicated false-positive-rate study, on benchmarks where destination-side consistency is load-bearing, as the proper way to quantify synchronization's contribution. (The overall full-pipeline false-positive rate is analyzed separately in Section~\ref{sec:discussion}.)

\subsection{RQ3: Parameter Sensitivity}

We evaluate the sensitivity of BridgeSentry to three key parameters: the number of retrieved exploits ($k$) in the RAG module, the waypoint reward weight ($\beta$), and the time budget ($T$). The default configuration uses $k = 3$, $\beta = 0.4$, and $T = 60$\,s. We sweep $k \in \{1,3,5,10\}$ and $\beta \in \{0.1,0.4,0.7\}$ (real-bytecode, 5 runs $\times$ 12 bridges per setting), and derive the $T$ curve from the time-to-violation distribution of the 240-run main sweep. Table~\ref{tab:sensitivity} summarizes $k$ and $\beta$; Table~\ref{tab:tbudget} reports $T$.

\begin{table}[t]
\centering
\caption{Sensitivity to RAG retrieval depth $k$ and waypoint weight $\beta$ (real-bytecode, 5 runs $\times$ 12 bridges per setting). Detection, median TTE, and mean cross-chain coverage are essentially flat, indicating the pipeline is robust to both parameters on this benchmark.}
\label{tab:sensitivity}
\begin{tabular}{@{}llccc@{}}
\toprule
Param & Value & Bridges det. & Med.\ TTE & XCC\textsubscript{ATG} \\
\midrule
\multirow{4}{*}{$k$}
 & 1  & 12/12 & 0.71\,s & 100\% \\
 & 3  & 12/12 & 0.71\,s & 100\% \\
 & 5  & 12/12 & 0.70\,s & 100\% \\
 & 10 & 12/12 & 0.71\,s & 100\% \\
\midrule
\multirow{3}{*}{$\beta$}
 & 0.1 & 12/12 & 0.77\,s & 99.8\% \\
 & 0.4 & 12/12 & 0.78\,s & 100\% \\
 & 0.7 & 12/12 & 0.71\,s & 100\% \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[t]
\centering
\caption{Sensitivity to time budget $T$, derived from the 240-run main sweep. Detection accrues quickly: all 12 bridges are reached by $T=2$\,s and every run detects within 30\,s.}
\label{tab:tbudget}
\begin{tabular}{@{}lccccccc@{}}
\toprule
$T$ & 0.5\,s & 1\,s & 2\,s & 5\,s & 10\,s & 30\,s & 60\,s \\
\midrule
Bridges det. & 6/12 & 11/12 & 12/12 & 12/12 & 12/12 & 12/12 & 12/12 \\
Runs det.\ (\%) & 35 & 52 & 70 & 90 & 99.6 & 100 & 100 \\
\bottomrule
\end{tabular}
\end{table}

Two of the three parameters have \emph{negligible} effect. Varying RAG retrieval depth $k$ from 1 to 10 leaves detection at 12/12, median TTE at $\approx$0.71\,s, and cross-chain coverage at 100\%---the reconstructed bugs are reachable even when the scenario generator is grounded on a single retrieved exploit, so additional retrieved context does not change the outcome on this benchmark (it would matter more on previously-unseen bugs, which RQ1's analysis flags as the regime where guidance helps). The waypoint weight $\beta$ is likewise flat across $\{0.1,0.4,0.7\}$: because the ATG-derived scenarios already direct the fuzzer to the vulnerable region, the balance between coverage-driven and waypoint-driven reward is not the binding factor here. The one parameter that materially moves detection is the time budget $T$: detection rises from 6/12 bridges at 0.5\,s to 12/12 at 2\,s, with all runs detecting within 30\,s, so the 60\,s budget used throughout is comfortably sufficient and a 5\,s budget would already recover 90\% of runs. This robustness profile is consistent with the RQ1/RQ2 finding that detection saturates on reconstructed benchmarks; the sensitivity that remains is dominated by how long the fuzzer is allowed to run, not by the retrieval or reward hyperparameters.

\subsection{RQ4: Cross-Chain Coverage Analysis}

We measure cross-chain coverage (XCC) as the fraction of cross-chain paths exercised during fuzzing. Because the ATG is produced by BridgeSentry's own Module~1, reporting XCC solely against this ATG risks circular evaluation. We therefore compute two variants:

\begin{itemize}
    \item \textbf{XCC\textsubscript{ATG}}: Coverage measured against BridgeSentry's ATG-enumerated paths (internal metric).
    \item \textbf{XCC\textsubscript{S}}: An independent coverage metric measured against a cross-function call graph extracted by Slither~\cite{feist2019slither} from the same source contracts. We take the executed scenario actions as dynamic entry functions and compute the fraction of call-graph functions forward-reachable from them, so the denominator is fixed by Slither (not by our ATG).
\end{itemize}

\noindent Across all 12 benchmarks (240 real-bytecode runs, 20 per bridge), BridgeSentry exercises XCC\textsubscript{ATG} $= 100\%$ of the ATG-enumerated cross-chain edges, while genuinely executing contract bytecode on both EVMs (mean 483 / 485 basic blocks on source / destination). Edge attribution uses two complementary paths---direct \texttt{contract}-field match and a function-signature (bare-op) match against \texttt{edge.function\_signature}---so the metric credits an edge whenever the corresponding operation is exercised, even when the Module~2 scenario omits the owning contract. (An earlier instrumentation that relied on the \texttt{contract} field alone under-counted edges on real LLM scenarios, reaching only 66.7\% on Nomad; the function-signature path closes that gap, and the result is consistent with the 99\% obtained on mock fixtures.)

The independent XCC\textsubscript{S} metric paints a deliberately more conservative picture: across the 11 EVM-compilable benchmarks (Wormhole is excluded as its Solana-side source does not compile under Slither, consistent with its out-of-scope treatment elsewhere), BridgeSentry reaches a mean XCC\textsubscript{S} of $66.1\%$ of all Slither-enumerated functions, ranging from $14.3\%$ on Nomad---whose exploit is a single-function root-validation bypass that traverses few of the contract's 21 functions---to $100\%$ on Qubit. The gap between XCC\textsubscript{ATG} ($100\%$) and XCC\textsubscript{S} ($66.1\%$) is expected and informative: the Slither graph counts every function in the deployed contracts, including ERC-20 token internals, message-encoding helpers, and view functions that a given exploit need not traverse, whereas XCC\textsubscript{ATG} counts only the security-relevant cross-chain arcs. The two metrics therefore bound the coverage from both sides---full coverage of the cross-chain arcs that matter, and roughly two-thirds of the entire static function surface---and the independent denominator rules out the circularity concern.

Qualitatively, the cross-chain coverage advantage is also structural: single-chain fuzzers exercise 0\% of relay-mediated edges because they cannot drive the off-chain component at all, whereas BridgeSentry traverses source, relay, and destination arcs within one harness.

% ============================================================
\section{Discussion}\label{sec:discussion}
% ============================================================

\subsection{Limitations}

BridgeSentry has several limitations that merit discussion.

The semantic extraction module depends on the quality of the LLM's code understanding. For highly obfuscated or compiled-only contracts where source code is unavailable, ATG construction may be incomplete or inaccurate. The validation pipeline reduces unsupported LLM output, but it does not make the entire deployed bridge system fully verified. The protocol model is necessarily bounded, and symbolic execution can be limited by path explosion, external calls, and missing environmental assumptions. Stronger machine-checked specifications and deeper symbolic summaries remain important extensions.

The RAG module is bounded by the coverage of the exploit knowledge base; attacks that exploit vulnerability classes not represented in the 51 historical incidents will receive weaker scenario guidance. The embedding model, all-MiniLM-L6-v2, is a general-purpose sentence transformer and may not capture the structural nuances of Solidity code or EVM opcode traces with the same fidelity as a domain-specific embedding model.

The synchronized dual-EVM architecture currently supports only EVM-compatible chains. Extending to heterogeneous chain pairs, such as an EVM source chain and Solana's SVM destination chain, requires substantial additional engineering for state representation and snapshot management.

The global snapshot mechanism, while preventing inconsistent state exploration, introduces an artificial coupling between the two chain instances. Real-world blockchains operate asynchronously with independent block production, variable finality delays, and potential for MEV-driven timestamp manipulation. Although BridgeSentry models cross-chain timing through configurable relay delays and independent timestamp advancement as described in Section~\ref{sec:method}, it does not fully simulate the network-layer nondeterminism and validator incentive dynamics that produce the most complex temporal vulnerabilities. This is a fundamental limitation of any local simulation approach and motivates integration with testnet-based evaluation environments.

The LLM-based modeling stage introduces latency: Module~2 scenario generation was measured at roughly 8--9 minutes per bridge in representative cases (Nomad 8.2\,min, Qubit 8.9\,min) on the free NVIDIA NIM tier, with high run-to-run variance dominated by API latency rather than local compute (one bridge took $\approx$74\,min under rate-limiting). This modeling stage dominates the end-to-end analysis cost, since Module~3 reaches a violation in 1.72\,s on average. We use a self-hosted open-weight backend (\texttt{gpt-oss-120b} via NVIDIA NIM), which avoids per-token API cost but still incurs inference latency; per-token usage is not instrumented in the current pipeline, and a systematic comparison against proprietary and code-specialized models is left to future work.

Finally, the benchmark of 12 EVM-compatible exploits represents 23.5\% of the available 51-incident dataset. The selection criteria requiring verified source code and EVM compatibility exclude the most architecturally complex cross-chain interactions. Performance on heterogeneous-chain vulnerabilities and zero-day exploits remains to be evaluated.

\subsection{Threats to Validity}

Internal validity threats include potential errors in the benchmark reconstruction, such as missing contract dependencies or incorrect fork block numbers. We mitigate this by verifying each reconstruction against the documented exploit transaction hash and confirming that the original attack sequence reproduces the vulnerability on the forked state. A more fundamental internal-validity threat concerns benchmark fidelity: Module~3 executes real bytecode on forked mainnet state but is directed by ATG-derived scenarios rather than blind exploration, so a reconstruction that over-simplifies the vulnerable behavior could inflate the detected rate. We partially mitigate this by reconstructing each benchmark from the documented root cause, by executing against live forked state at the pre-attack block, and by reporting the stricter predicate-match criterion for baselines.

\paragraph{False-positive analysis.}
We characterize false positives at two granularities, using a mechanical and reproducible criterion rather than manual labeling: a reported violation \emph{instance} is a true positive (TP) iff its execution trace contains at least one successful on-chain step and the resulting cross-chain imbalance is material ($|\text{dest}-\text{source}| \ge 10^{15}$ wei, i.e. $\ge 10^{-3}$ token), and a false positive (FP) otherwise (the invariant fired without a successful execution that round, or only a sub-threshold/rounding imbalance). At the \emph{bug level} the false-positive rate is effectively zero: all 12 detections correspond to genuine reconstructed exploits, and each bridge produces hundreds of TP instances (e.g.\ 2{,}780 for Ronin, 1{,}098 for Qubit, 234 for Nomad). At the \emph{instance level}, however, across all 37{,}086 violation instances reported over the 240 runs, the strict FPR is $69.8\%$ (per-bridge range $27.6\%$ on Ronin to $96.1\%$ on pGALA): BridgeSentry over-reports per run, emitting many weak invariant trips alongside the strong ones. This is a genuine limitation of the current invariant set, but it does not affect detection: a trivial triage filter that retains only the executed-and-material instances discards $\approx70\%$ of the report volume while preserving at least one TP for every one of the 12 bridges. We report the strict instance-level FPR as the conservative figure and note that a ranking layer that surfaces executed-and-material violations first is the natural remedy; a manual per-instance audit aligning each TP with the documented root cause is left as complementary future work.

Statistical validity: we run 20 independent repetitions per benchmark for the stochastic dynamic tools. For BridgeSentry the detection outcome is deterministic across the 240 runs (12/12 on every run), so per-run variance on the detection metric is zero and a between-tool significance test on detection is not informative; we therefore frame the comparison through the qualitative capability gap (out-of-the-box cross-chain coverage) and the predicate-match criterion rather than through a detection-rate hypothesis test. The time-to-exploit, in contrast, does vary across seeds (per-bridge standard deviation up to 2.6\,s), and we report its mean and spread over the 20 runs. % TODO: if the ItyFuzz/GPTScan full sweep or the ablation sweep produces non-degenerate distributions, add non-parametric tests (Mann-Whitney U, Vargha-Delaney A12) there.

External validity threats concern generalizability. The benchmark covers 12 of the documented attacks, all on EVM-compatible chains. Performance on undocumented or zero-day vulnerabilities, on non-EVM chains (e.g., the Solana source side of Wormhole, which we treat as out of scope), and on bridge architectures not represented in the knowledge base may differ.

Construct validity threats relate to the XCC metric, which is computed against an ATG produced by BridgeSentry itself, and to the small number of cross-chain edges per ATG (2--8), which makes the 100\% XCC\textsubscript{ATG} an easy ceiling to hit. We mitigate the circularity by additionally reporting the independently constructed XCC\textsubscript{S} from Slither's cross-function call graph (mean 66.1\%), whose denominator does not depend on our ATG; the qualitative claim that single-chain baselines cover 0\% of relay-mediated edges likewise does not depend on the ATG construction.

\subsection{Future Work}

Several directions warrant investigation. Extending BridgeSentry to non-EVM chains, including Cosmos IBC and Solana, would broaden its applicability to the full cross-chain ecosystem. Incorporating formal verification for the synthesized invariants, either via bounded model checking or through integration with the EPG framework~\cite{qin2025epg}, would address the soundness limitations of LLM-generated invariants. A systematic comparison of LLM backends---proprietary GPT-4o-class models against the self-hosted open-weight model used here and code-specialized alternatives (e.g., DeepSeek-Coder-V2, Llama-3)---would characterize the trade-off between modeling quality, cost, and reproducibility. Adopting a domain-specific embedding model for the RAG module, such as a CodeBERT variant fine-tuned on Solidity, may improve retrieval precision for structurally similar exploits. A feedback loop from discovered vulnerabilities back into the knowledge base would enable continual learning. Finally, simulating realistic block-production nondeterminism and MEV-driven reordering within the dual-EVM harness would test BridgeSentry's robustness against temporal attack vectors beyond configurable relay delays.

% ============================================================
\section{Conclusion}\label{sec:conclusion}
% ============================================================

This paper presented BridgeSentry, a framework for proactive vulnerability discovery in cross-chain bridges that couples LLM-based semantic extraction, retrieval-augmented attack scenario generation, and synchronized dual-chain fuzzing. By adapting the Atomic Transfer Graph formalism~\cite{dubler2025atg} to model bridge protocol invariants and using historical exploit knowledge to guide scenario generation toward high-value vulnerability regions, BridgeSentry reaches all 12 reconstructed real-world exploits across 240 runs (20 per benchmark), including five off-chain key-compromise incidents that no baseline detects out of the box. The evidence supports a deliberately narrow claim: the enabling contributions are the synchronized dual-chain harness and the LLM-derived invariants, not a specific fuzzing-guidance heuristic. We show this directly---when the snapshot-based and directed-graybox baselines are re-implemented inside the same dual-chain harness, they too reach full detection, and the tools separate only under a stricter predicate-match criterion (SmartShot 12/12, XScope 10/12, VulSEye 9/12, SmartAxe 4/12), with the static analyzer's gap concentrated on runtime key-compromise cases that source-level analysis cannot resolve. We therefore do not claim a detection-rate advantage over baselines re-equipped with cross-chain modeling; we claim that coupling LLM-based protocol modeling with a synchronized dual-chain harness is what makes per-bridge cross-chain detection feasible at all, a capability absent from every tool in its published form. Detection runs as real-bytecode dual-EVM fuzzing on forked mainnet state, reaching a violation in 1.72\,s on average (per-bridge medians spanning 0.5\,ms to 4.9\,s). An ablation confirms the modules' role on a coverage metric---removing semantic extraction or RAG scenario generation collapses cross-chain coverage from 100\% to 2.6\% even though detection rate stays saturated, whereas desynchronizing the snapshot restore leaves coverage and the violated-invariant set unchanged (its effect is on cross-chain consistency, a false-positive concern this benchmark cannot isolate)---and a parameter-sensitivity study shows detection is robust to RAG depth $k$ and waypoint weight $\beta$, with the time budget being the only parameter that materially affects detection (all 12 bridges reached within 2\,s). The current evaluation is limited to EVM-compatible chains and a curated 12-exploit benchmark; extending to heterogeneous chain architectures, incorporating formal invariant verification, and a dedicated false-positive study to quantify synchronization's contribution are priority next steps.

% ============================================================
% References
% ============================================================

\begin{thebibliography}{28}

\bibitem{augusto2024sok}
A.~Augusto, R.~Belchior, M.~Correia, A.~Vasconcelos, L.~Zhang, and T.~Hardjono,
``SoK: Security and privacy of blockchain interoperability,''
in \textit{Proc. IEEE Symp. Security and Privacy (S\&P)}, 2024, pp.~3840--3865.

\bibitem{lee2023sok}
S.-S.~Lee, A.~Murashkin, M.~Derka, and J.~Gorzny,
``SoK: Not quite water under the bridge: Review of cross-chain bridge hacks,''
in \textit{Proc. IEEE Int. Conf. Blockchain and Cryptocurrency (ICBC)}, 2023, pp.~1--14.

\bibitem{liao2024smartaxe}
Z.~Liao, Y.~Nan, H.~Liang, S.~Hao, J.~Zhai, J.~Wu, and Z.~Zheng,
``SmartAxe: Detecting cross-chain vulnerabilities in bridge smart contracts via fine-grained static analysis,''
\textit{Proc. ACM Softw. Eng.}, vol.~1, no. FSE, 2024.

\bibitem{wu2025safeguarding}
J.~Wu, K.~Lin, D.~Lin, B.~Zhang, Z.~Wu, and J.~Su,
``Safeguarding blockchain ecosystem: Understanding and detecting attack transactions on cross-chain bridges,''
in \textit{Proc. ACM Web Conf.}, 2025, pp.~4902--4912.

\bibitem{lin2025bridgeshield}
D.~Lin, S.~Lu, Z.~Liu, J.~Wu, J.~Fang, K.~Lin, B.~Song, and Z.~Zheng,
``BridgeShield: Enhancing security for cross-chain bridge applications via heterogeneous graph mining,''
\textit{ACM Trans. Softw. Eng. Methodol.}, vol.~1, no.~1, 2025.

\bibitem{zhang2022xscope}
J.~Zhang, J.~Gao, Y.~Li, Z.~Chen, Z.~Guan, and Z.~Chen,
``Xscope: Hunting for cross-chain bridge attacks,''
in \textit{Proc. IEEE/ACM Int. Conf. Automated Software Engineering (ASE)}, 2022, pp.~1--4.

\bibitem{zhou2025bridgeguard}
Z.~Zhou, X.~Luo, X.~Ji, J.~Mao, and T.~He,
``BridgeGuard: Checking external interaction vulnerabilities in cross-chain bridge router contracts based on symbolic dataflow analysis,''
\textit{IEEE Trans. Dependable Secure Comput.}, 2025.

\bibitem{shou2023ityfuzz}
C.~Shou, S.~Tan, and K.~Sen,
``ItyFuzz: Snapshot-based fuzzer for smart contract,''
in \textit{Proc. 32nd ACM SIGSOFT Int. Symp. Software Testing and Analysis (ISSTA)}, 2023.

\bibitem{sun2024gptscan}
Y.~Sun, D.~Wu, Y.~Xue, H.~Liu, H.~Wang, Z.~Xu, X.~Xie, and Y.~Liu,
``GPTScan: Detecting logic vulnerabilities in smart contracts by combining GPT with program analysis,''
in \textit{Proc. IEEE/ACM 46th Int. Conf. Software Engineering (ICSE)}, 2024.

\bibitem{wei2025llm}
Z.~Wei, J.~Sun, Y.~Sun, Y.~Liu, and D.~Wu,
``Advanced smart contract vulnerability detection via LLM-powered multi-agent systems,''
\textit{IEEE Trans. Softw. Eng.}, 2025.

\bibitem{zhuang2021gnn}
Y.~Zhuang, Z.~Liu, P.~Qian, Q.~Liu, X.~Wang, and Q.~He,
``Smart contract vulnerability detection using graph neural networks,''
in \textit{Proc. 29th Int. Joint Conf. Artificial Intelligence (IJCAI)}, 2021, pp.~3283--3290.

\bibitem{liu2023gnn}
Z.~Liu, P.~Qian, X.~Wang, Y.~Zhuang, L.~Qiu, and X.~Wang,
``Combining graph neural networks with expert knowledge for smart contract vulnerability detection,''
\textit{IEEE Trans. Knowl. Data Eng.}, vol.~35, no.~2, pp.~1296--1310, 2023.

\bibitem{liang2025vulseye}
R.~Liang, J.~Chen, C.~Wu, K.~He, and Y.~Wu,
``VulSEye: Detect smart contract vulnerabilities via stateful directed graybox fuzzing,''
\textit{IEEE Trans. Inf. Forensics Security}, vol.~20, pp.~2157--2170, 2025.

\bibitem{ye2024midas}
M.~Ye, X.~Lin, Y.~Nan, J.~Wu, and Z.~Zheng,
``Midas: Mining profitable exploits in on-chain smart contracts via feedback-driven fuzzing and differential analysis,''
in \textit{Proc. 33rd ACM SIGSOFT Int. Symp. Software Testing and Analysis (ISSTA)}, 2024.

\bibitem{kong2025fuzzing}
Z.~Kong, C.~Zhang, M.~Xie, M.~Hu, Y.~Xue, and Y.~Liu,
``Smart contract fuzzing towards profitable vulnerabilities,''
\textit{Proc. ACM Softw. Eng.}, vol.~2, no. FSE, pp.~153--175, 2025.

\bibitem{qin2025epg}
K.~Qin, Z.~Ye, Z.~Wang, W.~Li, L.~Zhou, C.~Zhang, D.~Song, and A.~Gervais,
``Enhancing smart contract security analysis with execution property graphs,''
\textit{Proc. ACM Softw. Eng.}, vol.~2, no. ISSTA, pp.~1101--1122, 2025.

\bibitem{belchior2021survey}
R.~Belchior, A.~Vasconcelos, S.~Guerreiro, and M.~Correia,
``A survey on blockchain interoperability: Past, present, and future trends,''
\textit{ACM Comput. Surv.}, vol.~54, no.~8, pp.~1--41, 2021.

\bibitem{duan2023attacks}
L.~Duan, Y.~Sun, W.~Ni, W.~Ding, J.~Liu, and W.~Wang,
``Attacks against cross-chain systems and defense approaches: A contemporary survey,''
\textit{IEEE/CAA J. Autom. Sinica}, vol.~10, no.~8, pp.~1647--1667, 2023.

\bibitem{wu2024fuzzers}
S.~Wu, Z.~Li, L.~Yan, W.~Chen, M.~Jiang, and C.~Wang,
``Are we there yet? Unraveling the state-of-the-art smart contract fuzzers,''
in \textit{Proc. IEEE/ACM 46th Int. Conf. Software Engineering (ICSE)}, 2024.

\bibitem{lin2025connector}
D.~Lin, J.~Wu, Y.~Su, Z.~Zheng, and Y.~Nan,
``Connector: Enhancing the traceability of decentralized bridge applications via automatic cross-chain transaction association,''
\textit{IEEE Trans. Inf. Forensics Security}, 2025.

\bibitem{wang2019han}
X.~Wang, H.~Ji, C.~Shi, B.~Wang, Y.~Ye, P.~Cui, and P.~S.~Yu,
``Heterogeneous graph attention network,''
in \textit{Proc. World Wide Web Conf. (WWW)}, 2019, pp.~2022--2032.

\bibitem{chen2023semantic}
D.~Chen, L.~Feng, Y.~Fan, S.~Shang, and Z.~Wei,
``Smart contract vulnerability detection based on semantic graph and residual graph convolutional networks with edge attention,''
\textit{J. Syst. Softw.}, vol.~203, 2023.

\bibitem{chen2024gpufuzzing}
W.~Chen, X.~Luo, H.~Cai, and H.~Wang,
``Towards smart contract fuzzing on GPUs,''
in \textit{Proc. IEEE Symp. Security and Privacy (S\&P)}, 2024.

\bibitem{liang2025smartshot}
R.~Liang, J.~Chen, R.~Cao, K.~He, R.~Du, and S.~Li,
``SmartShot: Hunt hidden vulnerabilities in smart contracts using mutable snapshots,''
\textit{Proc. ACM Softw. Eng.}, vol.~2, no. FSE, 2025.

\bibitem{li2025blockchain}
N.~Li, M.~Qi, Z.~Xu, X.~Zhu, W.~Zhou, S.~Wen, and Y.~Xiang,
``Blockchain cross-chain bridge security: Challenges, solutions, and future outlook,''
\textit{Distrib. Ledger Technol.: Res. Pract.}, vol.~4, no.~1, pp.~1--34, 2025.

\bibitem{dubler2025atg}
S.~D\"ubler, F.~Badaloni, P.~Moreno-Sanchez, and C.~Schneidewind,
``Atomic transfer graphs: Secure-by-design protocols for heterogeneous blockchain ecosystems,''
in \textit{Proc. IEEE Computer Security Foundations Symp. (CSF)}, 2025, pp.~300--315.

\bibitem{ali2025crossguard}
G.~M.~A.~Ali, H.~Chen, Z.~Wang, and C.~Du,
``CrossGuard: Runtime-adaptive LLM fuzzing for cross-contract vulnerabilities detection,''
\textit{Concurrency Comput.: Pract. Exper.}, 2025.

\bibitem{feist2019slither}
J.~Feist, G.~Grieco, and A.~Swende,
``Slither: A static analysis framework for smart contracts,''
in \textit{Proc. IEEE/ACM 2nd Int. Workshop on Emerging Trends in Software Engineering for Blockchain (WETSEB)}, 2019, pp.~8--15.

\end{thebibliography}

\end{document}
